---
title: "2M3: Probability that the globe was Earth given land observation."
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 5.5,
  fig.height = 3.5
)
```
Suppose there are two globes, one for Earth and one for Mars. 

The Earth globe is 70% covered in water. 

The Mars globe is 100% land. 

Further suppose that one of these globes - you do not know which - was tossed in the air and produced 
a "land" observation. Assume that each globe was equally likely to be tossed. 

Show that the posterior probability that the globe was the Earth, conditional on seeing "land" is $Pr(Earth|land) = 0.23$.

```{r message=FALSE }
library(dplyr)
library(ggplot2)

p_land_Earth <- 0.3
p_land_Mars <- 1.0
p_Earth <- 0.5
p_Mars <- 0.5

# We use Bayes' theorem to compute the posterior probability

P = (p_land_Earth * p_Earth) / 
    ((p_land_Earth * p_Earth) + (p_land_Mars * p_Mars))

print(P)

```

We use the Bayes' theorem formula:

$$
\text{Pr(Earth | land)} = \frac{\text{Pr(land|Earth) Pr(Earth)}}{\text{Pr(land|Earth) Pr(Earth) + Pr(land|Mars) Pr(Mars)}} = \frac{0.3 \times 0.5}{0.3 \times 0.5 + 1 \times 0.5} = 0.23
$$
